---
title: "Assignment 1"
---

# Assignment 1

```{r}
1 + 1
```

My first assignment has two parts.

## (a)

**I choosed 'Veri Bilimi ve Endüstri Mühendisliği Üzerine Sohbetler -Kerem Demirtaş & Erdi Daşdemir'**

**1 Question: Why is Domain Knowledge considered indispensable for a data scientist when defining a problem?**

An engineer who doesn't understand the dynamics behind the data will misdiagnose the problem, leading to misleading and irrelevant conclusions.

**2 What was the key solution that helped salvage aircraft during World War II?**

A\) Reinforcing parts of aircraft showing the most bullet holes.

B\) Increasing the aircraft's speed to avoid being shot down.

C\) Reinforcing parts of aircraft without bullet holes, based on data from aircraft that did not return.

D\) Using distributed computation to predict enemy fire patterns.

E\) Reinforcening aircraft cockpit parts to protect the pilot.

Correct Answer: C

## (b)

```{r}
library(dslabs)
data("polls_us_election_2016")
my_first <- "Cihan"
my_birth_year <- 2003
k <- (nchar(my_first) + my_birth_year) %% 15 + 8
if (k %% 2 == 0) head(polls_us_election_2016, k) else tail(polls_us_election_2016, k)

# 1. NA Analizi
sum(is.na(polls_us_election_2016))
sort(colSums(is.na(polls_us_election_2016)), decreasing = TRUE)[1:8]

# 2. NA Değiştirme (new_data objesine)
new_data <- polls_us_election_2016

for(i in 1:ncol(new_data)) {
  if(is.numeric(new_data[[i]])) {
    new_data[[i]][is.na(new_data[[i]])] <- my_birth_year + k
  } else {
    new_data[[i]] <- as.character(new_data[[i]])
    new_data[[i]][is.na(new_data[[i]])] <- paste0(my_first, "_", k)
  }
}

if (k %% 2 == 0) head(new_data, k) else tail(new_data, k)
sum(is.na(new_data))
anyNA(new_data)
```

AI assistance was used when writing the for function..

\- Yukarıda gördüğün Taski incele ve bana aşsağıda yazdığım kodun eksikliğini giderecek şekilde taski bitir. - Koddaki fonksiyon isimlerini düzenle herkesin anlayacağı hale getir.

```{r}
library(dslabs)

data("polls_us_election_2016")

my_first = "Cihan"
my_birth_year = 2003

name_length = nchar(my_first)

k = (name_length + my_birth_year) %% 15 + 8

if (k %% 2 == 0) {
  head(polls_us_election_2016 , k)
} else {
  tail(polls_us_election_2016 , k)
}
```

\
